Mutual Modelling

### 2015-06-17 mutual-modeling.tex
Review by Pierre

    Building on a set of five independent studies that where conducted over
    several years, we propose in this article a simple model of the mechanisms
    of mutual modelling. It integrates several concepts related to the classical
    idea of knowledge grounding, and we apply it as an operational tool to
    analyse the interplay of learning and mutual modelling in the five studies.

@@

From its very beginning, CSCL research has been following
\citet{roschelle1995construction} suggestion that collaborative learning has
something to do with the process of constructing and maintaining a \emph{shared
understanding} of the task at hand. Building a shared/mutual understanding
refers to the upper class of collaborative learning situations, those in which
students should build upon each other's understanding to refine their own
understanding: what is expected to produce learning is not the mere fact that
two students build the same understanding but the cognitive effort they have to
engage to build this shared understanding~\citep{schwartz1995emergence}. This
effort can be observed by the frequency of rich interactions, \ie interactions
whose occurrence has been related to learning: (self-) explanations in cognitive
science~\citep{chi1989self, webb1991task}, conflict resolution in
socio-cognitive theories~\citep{doise1975social},
mutual regulation~\citep{blaye1995collaborative} in a Vygostkian perspective, etc. The
construction of a shared understanding has been investigated for several years
in psycholinguistics, under the  notion of
\emph{grounding}~\citep{clark1986referring}. However, the relevance of grounding
mechanisms for explaining learning outcomes has been questioned in learning
sciences. The monitoring and repair of misunderstanding explains for instance
referential failures in short dialogue episodes but does hardly predict
\emph{conceptual change} (\ie the acquisition, acceptation and integration of a
new belief into one's mental model) over longer
sessions~\cite{dillenbourg2006sharing}. The cumulative effect of grounding
episodes can probably be better understood from a socio-cultural perspective:

@@

Besides, we have different levels of mutual modelling. If $A$ states ``B thinks I am good in
maths'', $A$ builds a \emph{second level} model:
\model{A}{B}{\M{B}{A}{\text{maths-skill}}}. This leads to possibly infinite
regress of nested models: $A$
saying ``$B$ knows that I don't expect him to solve this statistics problem''
corresponds to \model{A}{B}{\M{B}{A}{\M{A}{B}{\text{statistic-skills}}}}.

@@

    \item Tasks vary a lot with respect to how much they require mutual
        understanding.  The \emph{grounding criterion} -- denoted
        \groundingcriterion -- refers to how important it is to mutually share a
        piece of information $X$ to succeed the task $T$. It can be calculated as
        the probability to succeed $T$ despite the fact $X$ is not grounded.
        $\mathcal{M}^{\circ}_{min}(A,B,X)$ can be estimated from the correlation
        between \Model{A}{B}{X} and the task performance.

@@

\begin{multline} \label{eq:probrepair}
    p(\alpha_{t_1}(X,T) / \mathcal{M}^{\circ}_{t_2}(A,B,X) \nearrow) \propto \\
    \frac{\mathcal{M}^{\circ}_{min}(A,B,X,T) - \mathcal{M}^{\circ}_{t_1}(A,B,X)}{cost (\alpha)}
\end{multline}

@@

    \begin{enumerate}
        \item \model{A}{B}{emotion}: how accurately $A$ perceives $B$'s emotional state
            (study 3),

@@

@@

    \item $\mathcal{M}^{\circ}_{t1}(A,B,X)$: along the same reasoning, the initial degree
        of common grounds should be rather low (and hence the difference between
        initial and required degrees rather high) in order to make mutual
        modelling effort more observable. Studies 1, 4 and 5 have been conducted
        with teams of students who did not know each other. They came
        nonetheless from the same university (and they hence had some general common
        grounds).  For studies 2 and 3, students knew each other before for
        reasons explained later on. In study 5, we manipulated the initial mutual modelling by
        using a {\sc jigsaw} script.

@@

\begin{itemize}
    \item {\bf Capturing \model{A}{B}{X}}: The simplest method is to ask $A$
        what he/she believes about what $B$ knows, feels, intends to do, etc.
        This raises obvious methodological concerns since such a question
        triggers a modelling process beyond what would naturally occur. To avoid
        this bias, one can estimate mutual modelling after task completion.
        Then, the obvious drawback are memory losses and by post-hoc
        reconstruction.  The first method was used in study 2 and the second one
        in the other studies. Another option would be to rely on external
        behavioural metrics like eye-tracking: we hypothesise for instance that
        the fixation time reflects the efforts engaged by the human to
        understand, hence, model, the others. Such an approach has however not
        yet been investigated in the presented studies.

@@

\subsubsection*{Studies}

@@

$\mathcal{H}_{2}$ is also called a second level modelling hypothesis since $B$
needs to monitor $A$ to see if $A$ understood him/her
($\mathcal{M}(B,A,\mathcal{M}(A,B))$).

@@

One interesting question relates to the symmetry of mutual modelling: what is
the relationship between \Model{A}{B}{X} and
\Model{B}{A}{X} (Fig.~\ref{mm_symmetry})? A low symmetry would mean that mutual modelling is mainly an
individual attitude/aptitude ($\mathcal{H}_{1}$). A high correlation might
support $\mathcal{H}_{2}$ since there is a low probability that randomly formed
pairs integrate peers with the same level of mutual modelling skills.

@@

Conversely, does $C$ model more accurately $A$ than $B$ ($\Delta_3=
\Delta(\mathcal{M}^{\circ}(C,A,X),
\mathcal{M}^{\circ}(C,B,X))$)? A positive answer would support $\mathcal{H}_{3}$.

@@

In order to evaluate \gModel{A}{B} during the task, we used two questionnaires
(Fig.~\ref{study1:questionnaires}) that were displayed during each of the three
games, as a transparent layer appearing over the game display. The first
questionnaire concerned the player's intended actions. The second questionnaire
asked each player about what he thought her or his partner was intending to do.
Some answers were identical in both questionnaires (like ``adjusting a shot'')
while others were reversed (``to guide my partner'' versus ``to guide me''). We
chose a subjective measure of accuracy ($\Delta(\M{A}{A}{X}, \M{A}{B}{X})$)
rather than an objective measure (\ie the model \gmodel{A}{B} is compared to $B$'s
next action) because some of the activities proposed by the questionnaire were not
observable by the environment (\eg establishing a strategy). We calculated
\Model{A}{B}{activity_{game_{i}}}) as the number of common answers between
questionnaires \gmodel{A}{A} and \gmodel{A}{B} in each game and computed the
average value a across the 3 levels.

@@

@@

How to interpret a correlation of 0.38 between \gModel{A}{B} and \gModel{B}{A}?
If it was null, modelling would be interpreted as an individual process that
varies according to personality traits or cognitive skills: some persons tend to
model more accurately their peer while others don't care or can simply not. If
the correlation was close to 1, we could conclude that the modelling accuracy is
an emergent property of teams since there would be low probability that, by
chance, low accurate modellers are paired with accurate modellers and
conversely. Our correlation is between these two extremes but the very notion of
significant intra-class correlation tend to indicate that one may not consider
peers as independent subjects, which is an argument for the \emph{interaction}
hypothesis $\mathcal{H}_{3}$.

@@

\begin{figure*}[h!t]
        \centering
        \begin{subfigure}{.4\textwidth}
            \includegraphics[width=\linewidth]{image6.png}
            \caption{A's drawing of $B$'s path.}
        \end{subfigure}
        \begin{subfigure}{.4\textwidth}
            \includegraphics[width=\linewidth]{image7.png}
            \caption{Actual path followed by $B$.}
        \end{subfigure}
        \caption{Reported and actual path of one of the player, during the {\sc
        CatchBob} game.}
        \label{study2:paths}
\end{figure*}

@@

The aim of this unpublished\footnote{The data and statistical analyses of this
study are available online:
\url{https://github.com/chili-epfl/mutual-modelling-adoption-homosexuality-study}.}
study was to evaluate the effect of media richness on \Model{A}{B}{emotions}.
The hypothesis was that video communication would lead to a better \gModel{A}{B}
than audio only since emotions often impact on facial expressions.

\begin{figure*}[ht!]
        \centering
        \includegraphics[width=0.8\textwidth]{image8.jpg}
        \caption{Example of argumentation graph}
        \label{study3:argumentation_graph}
\end{figure*}

@@

\paragraph{Grounding criterion} The maps produced by teams were ranked by three
independent judges on completeness and structure quality (Kendall's $W=0.474$,
limited agreement). We used the average rank as a estimation of the team
performance and correlated it with the average of the 6 values of \gModel{A}{B}
per team (\gModel{A}{B}, \gModel{A}{C}, \gModel{B}{A},...). The correlation is
-0.22: teams with a good \gModel{A}{B} tend to be better ranked.

@@

A t-test on the two sets releaved a significantly lower average difference in
the experimental data (mean difference: $0.40$ vs $0.54$ with random gradings,
$t=-3.3, df=60, p = 0.0016$), supporting the symmetry hypothesis.

\paragraph{Triangle questions} $\Delta_2$ is computed in a similar way as the average of
the absolute differences between \gModel{A}{C} and \gModel{B}{C} over the 60
subjects. The average difference is 0.42 ($SD= 0.34$), and if not significantly
different from the same data obtained from random gradings ($t=-1.61, df=60,
p=0.11$).

For $\Delta_3$, the average absolute difference between \gModel{C}{A} and
\gModel{C}{B} over the 60 subjects is 0.40 ($SD= 0.41$) and is significantly
lower than chance ($t=-2.62, df=60, p=0.01$): a given subject tends to model its
two partners with similar degrees of accuracy, which supports $\mathcal{H}_{1}$.

\begin{figure*}[ht!]
        \centering
        \includegraphics[width=0.9\textwidth]{image9.pdf}
        \caption{Average values of \Model{A}{B}{X} where $X$ is one of the proposed
        emotions (max = 7).}
        \label{study3:deg_m_values}
\end{figure*}

@@

\begin{figure*}
    \centering
    \begin{tikzpicture}[scale=0.8]
        \node[anchor=south west,inner sep=0] at (0,0)
            {\includegraphics[width=0.75\textwidth]{image10.png}};

            \node[rectangle,draw, thick] at (10,5.4) {Self map};
            \node[rectangle,draw, thick] at (7.5,3.3) {Partner map};
            \node[rectangle,draw, thick] at (2.5,1.5) {Collaborative map};
    \end{tikzpicture}
    \caption{The group concept map and the individual concept maps in study
    4}
    \label{study4:concept_map}
\end{figure*}

@@

The independent variable, script versus no-script, was implemented by the
difference of texts that individuals had to read.  The dependent variables were
the post-test scores, used to assess \Model{A}{B}{knowledge}. In phase 6,
participants were ask to estimate (7-point Likert scale) their own and their
partner's outcome knowledge with respect to each chapter of the learning
material. The order of questions about oneself and about the other was
counterbalanced across participants. We measure \gModel{A}{B} in an objective
(Eq.~\ref{eq:study4.1} and \ref{eq:study4.2}) as well as in a subjective way
(Eq.~\ref{eq:study4.3}).

\begin{multline} \label{eq:study4.1}
    \Mdeg{A}{B}{knowledge} = 
        \sum_{i=1}^{3} (\M{A}{B}{chapter_i} - score(B, chapter_i))
\end{multline}

\begin{multline} \label{eq:study4.2}
    \Mdeg{A}{A}{knowledge} = 
        \sum_{i=1}^{3}  (\M{A}{A}{chapter_i} - score(A, chapter_i))
\end{multline}

\begin{multline} \label{eq:study4.3}
    \Mdeg{A}{B}{knowledge} = 
        \sum_{i=1}^{3}  (\M{A}{B}{chapter_i} - \M{B}{A}{chapter_i})
\end{multline}

@@

In this experiment, the symmetry of mutual modelling is only found when subjects
are in conditions of symmetry of information. This consolidates the hypothesis
of \gModel{A}{B} being a property of interactions in context rather than $A$'s
cognitive attitude.

@@

\begin{table*}[ht!]
\centering
\resizebox{\textwidth}{!}{%
\begin{tabular}{p{2.6cm}|p{3.5cm}|p{3.5cm}|p{3.5cm}|p{3.5cm}|p{3.5cm}}
\textit{}                     & \textbf{Study 1}                 & \textbf{Study 2}                & \textbf{Study 3}          & \textbf{Study 4}          & \textbf{Study 5}             \\ \hline
\textbf{Task}                 & Game in virtual space            & Game in physical space          & Building an argument map  & Building a concept map    & Building a concept map       \\
\textbf{Interactions}         & Audio                            & Written                         & Audio / Video             & Audio                     & Audio                        \\
\textbf{Shared editor}        & 3D Space                         & 2D Map                          & Concept Map               & Concept Map               & Concept Map                  \\
\textbf{Group Size}           & dyads                            & \textbf{triads}                 & \textbf{triads}           & dyads                     & dyads                            \\
\textbf{Duration (mean)}      & 90min                            & 16min                           & 61min                     & 90min                     & 90min                        \\
\textbf{Awareness tool}       & Partner's position               & Partner's current/past pos.     & -                         & Partner's concept map     & Partner's scores at pre-test \\
\textbf{Dependent var.}       & Team/Ind. performance            & Team/Ind. performance           & Team performance          & Team/Ind. knowledge       & Team/Ind. knowledge          \\
\textbf{Independent var.}     & Awareness tool \textit{vs} none  & Awareness tool \textit{vs} none & Audio \textit{vs} Audio+Video & Script \textit{vs} none & Awareness tool \textit{vs} none       \\
\textbf{Grounding crit.}      & +0.42                            & +0.15                           & +0.22                     & +0.08                     & +0.40                        \\
$\mathcal{H}_1$               &                                  & supported                       & supported                 &                           &                              \\
$\mathcal{H}_2$               &                                  & supported                       & supported                 &                           &                              \\
$\mathcal{H}_3$               & supported                        & supported                       &                           & supported                 &                              \\
\end{tabular}
}
\caption{Comparison of the studies}
\label{synthesis_table}
\end{table*}

@@

The triangular questions lead to similar contradictions. The $\Delta_2$
correlation between the \gmodel{A}{C} and \gmodel{B}{C} (study 2)
support $\mathcal{H}_{2}$ if modelling skills were purely individual, there would
be no reason for modelling skills of $A$ and $B$ to be correlated.  The role of $C$ in
\gmodel{A}{C} and \gmodel{B}{C} probably explains this correlation.  Conversely,
the $\Delta_3$ correlation between the \gmodel{A}{B} and \gmodel{A}{C} (study
3) question $\mathcal{H}_{3}$: if the role of the modellee was so
important, it would be surprising to have by chance a correlation between
$B$'s and $C$' ability to drive $A$'s modelling.

In addition, the lack of correlation between \gmodel{A}{A} and \gmodel{A}{B}
($\Delta_4$ in study 4 and study 5) could also contributes to the idea that $A$'s
modelling skills is not the key factor. However, between modelling someone and
modelling oneself, \ie  metacognition, they are so many differences, that we
would hardly conclude from that.

>>>>

    Building on a set of five independent studies that where conducted over
    several years, we propose in this article a simple model of the mechanisms
    of mutual modelling. It integrates several concepts related to the classical
    idea of grounding, and we apply it as an operational tool to
    analyse the interplay of learning and mutual modelling in the five studies.

@@

From its very beginning, CSCL research has been following
\citet{roschelle1995construction} suggestion that collaborative learning has
something to do with the process of constructing and maintaining a \emph{shared
understanding} of the task at hand. Building a shared/mutual understanding
refers to the upper class of collaborative learning situations, those in which
students should build upon each other's understanding to refine their own
understanding: what is expected to produce learning is not the mere fact that
two students build the same understanding but the cognitive effort they have to
engage to build this shared understanding~\citep{schwartz1995emergence}. This
effort can be observed by the frequency of rich interactions, \ie interactions
whose occurrence has been related to learning: (self-) explanations in cognitive
science~\citep{chi1989self, webb1991task}, conflict resolution in
socio-cognitive theories~\citep{doise1975social},
mutual regulation~\citep{blaye1995collaborative} in a Vygostkian perspective, etc. The
construction of a shared understanding has been investigated for several years
in psycholinguistics, under the  notion of
\emph{grounding}~\citep{clark1986referring}. However, the relevance of grounding
mechanisms for explaining learning outcomes has been questioned in learning
sciences. The monitoring and repair of misunderstanding explains for instance
referential failures in short dialogue episodes but does hardly predict
\emph{conceptual change} (\ie the acquisition, acceptation and integration of a
new belief into one's mental model) over longer
sessions~\citep{dillenbourg2006sharing}. The cumulative effect of grounding
episodes can probably be better understood from a socio-cultural perspective:

@@

Besides, we have different levels of mutual modelling. If $A$ states ``B thinks I am good in
maths'', $A$ builds a \emph{second level} model:
\model{A}{B}{\M{B}{A}{\text{maths-skill}}}. This leads to possibly infinite
regress of nested models: $A$
saying ``$B$ knows that I don't expect him to solve this statistics problem''
corresponds to \\ \model{A}{B}{\M{B}{A}{\M{A}{B}{\text{statistic-skills}}}}.

@@

    \item Tasks vary a lot with respect to how much they require mutual
        understanding.  The \emph{grounding criterion} -- denoted
        \groundingcriterion -- refers to how accurate the models need to be to
        succeed the task $T$. It can be calculated as the probability to succeed
        $T$ despite the fact $X$ is not grounded.
        $\mathcal{M}^{\circ}_{min}(A,B,X)$ can be estimated from the correlation
        between \Model{A}{B}{X} and the task performance.

@@

\begin{multline} \label{eq:probrepair}
    p(\alpha_{t_1}(X,T) / \mathcal{M}^{\circ}_{t_2}(A,B,X) \nearrow) \simeq
    \frac{\mathcal{M}^{\circ}_{min}(A,B,X,T) - \mathcal{M}^{\circ}_{t_1}(A,B,X)}{cost (\alpha)}
\end{multline}

@@

@@

        \item \model{A}{B}{emotion}: how accurately $A$ perceives $B$'s emotional state
            (study 3),

@@

    \item $\mathcal{M}^{\circ}_{t0}(A,B,X)$: along the same reasoning, the initial degree
        of common grounds should be rather low (and hence the difference between
        initial and required degrees rather high) in order to make mutual
        modelling effort more observable. Studies 1, 4 and 5 have been conducted
        with teams of students who did not know each other. They came
        nonetheless from the same university (and they hence had some general common
        grounds).  For studies 2 and 3, students knew each other before for
        reasons explained later on. In study 5, we manipulated the initial mutual modelling by
        using a {\sc jigsaw} script.

@@

\begin{itemize}
    \item {\bf Capturing \model{A}{B}{X}}: The simplest method is to ask $A$
        what he/she believes about what $B$ knows, feels, intends to do, etc.
        This raises obvious methodological concerns since such a question
        triggers a modelling process beyond what would naturally occur. To avoid
        this bias, one can estimate mutual modelling after task completion.
        Then, the obvious drawback are memory losses and by post-hoc
        reconstruction.  The first method was used in study 2 and the second one
        in the other studies. Another option would be to rely on external
        behavioural metrics like eye-tracking: we hypothesise for instance that
        the fixation time reflects the efforts engaged by the human to
        understand, hence, model, the others. Such an approach has however not
        been investigated in the presented studies.

@@

\subsubsection*{Hypotheses}

@@

$\mathcal{H}_{2}$ relates to second level modelling since $B$ needs to monitor
$A$ to see if $A$ understood him/her ($\mathcal{M}(B,A,\mathcal{M}(A,B))$). We
will see that $\mathcal{H}_{2}$ and $\mathcal{H}_{3}$ are actually difficult to
differentiate.

@@

One interesting question relates to the symmetry of mutual modelling: what is
the relationship between \Model{A}{B}{X} and \Model{B}{A}{X}
(Fig.~\ref{mm_symmetry})? A low symmetry would mean that mutual modelling is
mainly an individual attitude/aptitude ($\mathcal{H}_{1}$). A high correlation
might support $\mathcal{H}_{2}$ or $\mathcal{H}_{3}$ since there is a low
probability that randomly formed pairs integrate peers with the same level of
mutual modelling skills.

@@

Conversely, does $C$ model more accurately $A$ than $B$ ($\Delta_3=
\Delta(\mathcal{M}^{\circ}(C,A,X), \mathcal{M}^{\circ}(C,B,X))$)? A positive
answer would support $\mathcal{H}_{3}$. A negative answer would support
$\mathcal{H}_{2}$ since $\Delta_3$ could mainly be explained by the way $A$ and
$B$ help $C$ to model them.

@@

In order to evaluate \gModel{A}{B} during the task, we used two questionnaires
(Fig.~\ref{study1:questionnaires}) that were displayed during each of the three
games, as a transparent layer appearing over the game display. The first
questionnaire concerned the player's intended actions. The second questionnaire
asked each player about what he thought her or his partner was intending to do.
Some answers were identical in both questionnaires (like ``adjusting a shot'')
while others were reversed (``to guide my partner'' versus ``to guide me'').
This method provides us with a subjective measure of accuracy
($\Delta(\M{A}{A}{X}, \M{A}{B}{X})$) rather than an objective measure (\ie the
model \gmodel{A}{B} is compared to $B$'s next action) because some of the
activities proposed by the questionnaire were not observable by the environment
(\eg establishing a strategy). We calculated \Model{A}{B}{activity})
as the number of common answers between questionnaires \gmodel{A}{A} and
\gmodel{A}{B} in each game and computed the average value a across the 3 levels.

@@

\subsubsection*{The triangle and rectangle questions are not addressed in this study.}

@@

How to interpret a correlation of 0.38 between \gModel{A}{B} and \gModel{B}{A}?
If it was null, modelling would be interpreted as an individual process that
varies according to personality traits or cognitive skills: some persons tend to
model more accurately their peer while others don't care or can simply not
($\mathcal{H}_{1}$). If the correlation was close to 1, we could conclude that
the modelling accuracy is an emergent property of teams since there would be low
probability that, by chance, low accurate modellers are paired with accurate
modellers and conversely ($\mathcal{H}_{2}$). Our correlation is between these
two extremes but the very notion of significant intra-class correlation tend to
indicate that one may not consider peers as independent subjects, which is an
argument for the \emph{interaction} hypothesis $\mathcal{H}_{3}$.

@@

\begin{figure*}[h!t]
        \centering
        \begin{subfigure}{.45\textwidth}
            \includegraphics[width=\linewidth]{image6.png}
            \caption{A's drawing of $B$'s path.}
        \end{subfigure}
        \begin{subfigure}{.4\textwidth}
            \includegraphics[width=\linewidth]{image7.png}
            \caption{Actual path followed by $B$.}
        \end{subfigure}
        \caption{Reported and actual path of one of the player, during the {\sc
        CatchBob} game.}
        \label{study2:paths}
\end{figure*}

@@

The aim of this unpublished\footnote{The data and statistical analyses of this
study are available online:
\url{https://github.com/chili-epfl/mutual-modelling-emotions-study}.}
study was to evaluate the effect of media richness on \Model{A}{B}{emotions}.
The hypothesis was that video communication would lead to a better \gModel{A}{B}
than audio only since emotions often impact on facial expressions.

\begin{figure*}[ht!]
        \centering
        \includegraphics[width=\textwidth]{image8.jpg}
        \caption{Example of argumentation graph}
        \label{study3:argumentation_graph}
\end{figure*}

@@

\paragraph{Grounding criterion} The maps produced by teams were ranked by three
independent judges on completeness and structure quality (Kendall's $W=0.474$,
limited agreement). We used the average rank as a estimation of the team
performance and correlated it with the average of the 6 values of \gModel{A}{B}
per team (\gModel{A}{B}, \gModel{A}{C}, \gModel{B}{A},...). The correlation is
0.22: teams with a good \gModel{A}{B} tend to be better ranked.

@@

A t-test on the two sets releaved a significantly lower average difference in
the experimental data (mean difference: $0.40$ vs $0.54$ with random gradings,
$t=-3.3, df=60, p = 0.0016$), supporting $\mathcal{H}_{2}$ or $\mathcal{H}_{3}$.

\paragraph{Triangle questions} $\Delta_2$ is computed in a similar way as the average of
the absolute differences between \gModel{A}{C} and \gModel{B}{C} over the 60
subjects. The average difference is 0.42 ($SD= 0.34$), and if not significantly
different from the same data obtained from random gradings ($t=-1.61, df=60,
p=0.11$). This rejects $\mathcal{H}_{2}$.

For $\Delta_3$, the average absolute difference between \gModel{C}{A} and
\gModel{C}{B} over the 60 subjects is 0.40 ($SD= 0.41$) and is significantly
lower than chance ($t=-2.62, df=60, p=0.01$): a given subject tends to model its
two partners with similar degrees of accuracy, which supports $\mathcal{H}_{1}$.
It could also support $\mathcal{H}_{3}$, but it does not since $\Delta_2$ is not
significant.

\begin{figure*}[ht!]
        \centering
        \includegraphics[width=\textwidth]{image9.pdf}
        \caption{Average values of \Model{A}{B}{X} where $X$ is one of the proposed
        emotions (max = 7).}
        \label{study3:deg_m_values}
\end{figure*}

@@

\begin{figure*}
    \centering
    \begin{tikzpicture}[scale=1]
        \node[anchor=south west,inner sep=0] at (0,0)
            {\includegraphics[width=0.75\textwidth]{image10.png}};

            \node[rectangle,draw, thick] at (8,4.3) {Self map};
            \node[rectangle,draw, thick] at (6,2.6) {Partner map};
            \node[rectangle,draw, thick] at (2.5,1.5) {Collaborative map};
    \end{tikzpicture}
    \caption{The group concept map and the individual concept maps in study
    4}
    \label{study4:concept_map}
\end{figure*}

@@

The independent variable, script versus no-script, was implemented by the
difference of texts that individuals had to read.  The dependent variables were
the post-test scores, used to assess \Model{A}{B}{knowledge}. In phase 6,
participants were ask to estimate (7-point Likert scale) their own and their
partner's outcome knowledge with respect to each chapter of the learning
material. The order of questions about oneself and about the other was
counterbalanced across participants. 
%We measure \gModel{A}{B} in an objective
%(Eq.~\ref{eq:study4.1} and \ref{eq:study4.2}) as well as in a subjective way
%(Eq.~\ref{eq:study4.3}).
%
%\begin{multline} \label{eq:study4.1}
%    \Mdeg{A}{B}{knowledge} = 
%        \sum_{i=1}^{3} (\M{A}{B}{chapter_i} - score(B, chapter_i))
%\end{multline}
%
%\begin{multline} \label{eq:study4.2}
%    \Mdeg{A}{A}{knowledge} = 
%        \sum_{i=1}^{3}  (\M{A}{A}{chapter_i} - score(A, chapter_i))
%\end{multline}
%
%\begin{multline} \label{eq:study4.3}
%    \Mdeg{A}{B}{knowledge} = 
%        \sum_{i=1}^{3}  (\M{A}{B}{chapter_i} - \M{B}{A}{chapter_i})
%\end{multline}

@@

In this experiment, the symmetry of mutual modelling is only found when subjects
are in conditions of symmetry of information. This consolidates the hypothesis
of \gModel{A}{B} being a property of interactions in context ($\mathcal{H}_{3}$)
rather than $A$'s cognitive attitude.

@@

\begin{table*}[ht!]
\centering
\resizebox{\textwidth}{!}{%
\begin{tabular}{p{2.6cm}|p{3.5cm}|p{3.5cm}|p{3.5cm}|p{3.5cm}|p{3.5cm}}
\textit{}                     & \textbf{Study 1}                 & \textbf{Study 2}                & \textbf{Study 3}          & \textbf{Study 4}          & \textbf{Study 5}             \\ \hline
\textbf{Task}                 & Game in virtual space            & Game in physical space          & Building an argument map  & Building a concept map    & Building a concept map       \\
\textbf{Interactions}         & Audio                            & Written                         & Audio / Video             & Audio                     & Audio                        \\
\textbf{Shared editor}        & 3D Space                         & 2D Map                          & Concept Map               & Concept Map               & Concept Map                  \\
\textbf{Group Size}           & dyads                            & \textbf{triads}                 & \textbf{triads}           & dyads                     & dyads                            \\
\textbf{Duration (mean)}      & 90min                            & 16min                           & 61min                     & 90min                     & 90min                        \\
\textbf{Awareness tool}       & Partner's position               & Partner's current/past pos.     & -                         & Partner's concept map     & Partner's scores at pre-test \\
\textbf{Dependent var.}       & Team/Ind. performance            & Team/Ind. performance           & Team performance          & Team/Ind. knowledge       & Team/Ind. knowledge          \\
\textbf{Independent var.}     & Awareness tool \textit{vs} none  & Awareness tool \textit{vs} none & Audio \textit{vs} Audio+Video & Script \textit{vs} none & Awareness tool \textit{vs} none       \\
\textbf{Grounding crit.}      & +0.42                            & +0.15                           & +0.22                     & +0.08                     & +0.40                        \\
$\mathcal{H}_1$               &                                  & supported                       & supported                 &                           &                              \\
$\mathcal{H}_2$               &                                  & supported&                         &                           &                              \\
$\mathcal{H}_3$               & supported                        & supported                       &                           & supported                 &                              \\
\end{tabular}
}
\caption{Comparison of the studies}
\label{synthesis_table}
\end{table*}

@@

The triangular questions lead to similar contradictions. The $\Delta_2$
correlation between the \gmodel{A}{C} and \gmodel{B}{C} (study 2)
support $\mathcal{H}_{2}$ if modelling skills were purely individual, there would
be no reason for modelling skills of $A$ and $B$ to be correlated.  The role of $C$ in
\gmodel{A}{C} and \gmodel{B}{C} probably explains this correlation.  Conversely,
the $\Delta_3$ correlation between the \gmodel{A}{B} and \gmodel{A}{C} (study
3) question $\mathcal{H}_{2}$: if the role of the modellee was so
important, it would be surprising to have by chance a correlation between
$B$'s and $C$' ability to drive $A$'s modelling.

In addition, the lack of correlation between \gmodel{A}{A} and \gmodel{A}{B}
($\Delta_4$ in study 4 and study 5) could also contribute to the idea that $A$'s
modelling skills is not the key factor. However, between modelling someone and
modelling oneself, \ie  metacognition, they are so many differences, that we
would hardly conclude from that.
